\bf A Unitary RG-based Auxiliary Model Approach to Strongly-Correlated Electronic Systems

### 2023-07-19 TilingProjectDraft/tilingProject.tex
generated all of the plots again
jotted down points for pseudogap

\section{Momentum-space entanglement}

\begin{itemize}
	\item \(n_{\vec R_0}\rho n_{\vec R_0}\) + \(n_{\vec R_0 + \vec a}\rho n_{\vec R_0 + \vec a}\)
	\item \(e^{i \vec{q}\cdot\vec{a}}c^\dagger_{\vec R_0 + \vec a}c_{\vec R_0}\rho n_{\vec R_0}\) + h.c. + 
	      \(e^{-i \vec{q}\cdot\vec{a}}c^\dagger_{\vec R_0}c_{\vec R_0 + \vec a}\rho n_{\vec R_0}\) + h.c.
	\item \(c^\dagger_{\vec R_0 + \vec a}c_{\vec R_0 + \vec a}\rho n_{\vec R_0}\) + h.c.
	\item   \(e^{2i\vec{q}\cdot\vec{a}}c^\dagger_{\vec R_0 + \vec a}c_{\vec R_0}\rho c^\dagger_{\vec R_0 + \vec a}c_{\vec R_0}\) + h.c. + 
		\(c^\dagger_{\vec R_0}c_{\vec R_0 + \vec a}\rho c^\dagger_{\vec R_0 + \vec a}c_{\vec R_0}\) + h.c.
	\item \(e^{i \vec{q}\cdot\vec{a}} n_{\vec R_0 + \vec a}\rho c^\dagger_{\vec R_0 + \vec a}c_{\vec R_0}\) + h.c. + \(e^{-i \vec{q}\cdot\vec{a}} n_{\vec R_0 + \vec a}\rho c^\dagger_{\vec R_0}c_{\vec R_0 + \vec a}\) + h.c.
\end{itemize}
\subsection{\(k-\)space von-Neumann entropy}
The density matrix of the full Hamiltonian in ground-state is simply \(\rho_\text{gs} = \ket{\Psi_\text{gs}}\bra{\Psi_\text{gs}}\). In order to calculate entanglement measures in and among \(k-\)space states, we begin by obtaining an expression for the von-Neumann entropy of a \(\vec k-\)state, in terms of auxiliary model quantities. 
The full ground state \(\ket{\Psi_\text{gs}}\) can be written in the basis of the Fock states of momentum \(\vec k\sigma\):
\begin{equation}\begin{aligned}
	\Psi_\text{gs} = \sin\theta_{\vec k\sigma} \ket{n_{\vec k\sigma} = 0}\otimes\ket{\phi_{\vec k\sigma}} + \cos\theta_{\vec k\sigma} \ket{n_{\vec k\sigma} = 1}\otimes\ket{\bar\phi_{\vec k\sigma}}
\end{aligned}\end{equation}
where \(\ket{n_{\vec k\sigma}}\) is the state with occupancy \(n_{\vec k\sigma}\) from the Hilbert space of \(\vec k\sigma\). \(\ket{\phi_{\vec k\sigma}}\) and \(\ket{\bar\phi_{\vec k\sigma}}\) are the normalised states representing the configuration of the remaining degrees of freedom in the full state \(\Psi_\text{gs}\) when \(\hat n_{k\sigma}\) is 0 and 1 respectively. \(\sin \theta_{\vec k}\) and \(\cos\theta_{\vec k\sigma}\) are the probabilities of obtaining \(n_{\vec k\sigma}\) to be 0 and 1 respectively, in the full ground state.

@@

>>>>

\section{Momentum-space entanglement}
The density matrix of the full Hamiltonian in ground-state is simply \(\rho_\text{gs} = \ket{\Psi_\text{gs}}\bra{\Psi_\text{gs}}\). In order to calculate entanglement measures in and among \(k-\)space states, we begin by obtaining an expression for the von-Neumann entropy of a \(\vec k-\)state, in terms of auxiliary model quantities.

\subsection{\(k-\)space von-Neumann entropy}
The full ground state \(\ket{\Psi_\text{gs}}\) can be written in the basis of the Fock states of momentum \(\vec k\sigma\):
\begin{equation}\begin{aligned}
	\Psi_\text{gs} = \sin\theta_{\vec k\sigma} \ket{n_{\vec k\sigma} = 0}\otimes\ket{\phi_{\vec k\sigma}} + \cos\theta_{\vec k\sigma} \ket{n_{\vec k\sigma} = 1}\otimes\ket{\bar\phi_{\vec k\sigma}}
\end{aligned}\end{equation}
where \(\ket{n_{\vec k\sigma}}\) is the state with occupancy \(n_{\vec k\sigma}\) from the Hilbert space of \(\vec k\sigma\). \(\ket{\phi_{\vec k\sigma}}\) and \(\ket{\bar\phi_{\vec k\sigma}}\) are the normalised states representing the configuration of the remaining degrees of freedom in the full state \(\Psi_\text{gs}\) when \(\hat n_{k\sigma}\) is 0 and 1 respectively. \(\sin \theta_{\vec k}\) and \(\cos\theta_{\vec k\sigma}\) are the probabilities of obtaining \(n_{\vec k\sigma}\) to be 0 and 1 respectively, in the full ground state.

@@

\section{Emergence of effectively pseudogapped Anderson model at the MIT}
\begin{itemize}
\item The RG equation (in the weak coupling limit) of the \(J-U_b\) model that emerges in the Kondo limit of the eSIAM is similar to that of the pseudogapped Anderson model~\cite{fritzvojta2004} that has a bath density of states of the form \(|\omega|^\alpha\). If we define the dimensionless Kondo coupling \(g = \rho J\) and the dimensionless bath coupling \(u = \rho U_b\), the RG equation for \(g\),
\begin{equation}\begin{aligned}
	g \simeq g^2 + 4gu~,
\end{aligned}\end{equation}
can be mapped to the corresponding RG equation for the pseudogapped Kondo model,
\begin{equation}\begin{aligned}
	g = g^2 - \alpha g~,
\end{aligned}\end{equation}
with the identification \(\alpha = -4u = -4\rho U_b\).
\item Following the work by Si and Kotliar~\cite{kotliarsi_1993}, the impurity self-energy of the \(J-U_b\) model takes the form
	\begin{equation}\begin{aligned}
		\Sigma_{dd} \sim |\omega|^{\gamma_{dd}}~,
	\end{aligned}\end{equation}
	where the exponent \(\gamma_{dd}\) can be written in terms of the phase shifts (at the RG fixed point) \(\delta^*_\text{sp}\) and \(\delta^*_\text{ch}\) suffered by the conduction electrons due to the potentials \(J\) and \(U_b\) respectively in the Hamiltonian:
	\begin{equation}\begin{aligned}
		\gamma_{dd} = \frac{5}{4} - \left[ \frac{1}{\pi}\left( \delta^*_\text{sp} + \delta^*_\text{ch} \right) - \frac{1}{2}  \right]^2 - \left( \frac{\delta^*_\text{ch}}{\pi} \right)^2~.
	\end{aligned}\end{equation}
	The phase shifts are given by \(\delta^*_\text{sp}=\arctan\left( \pi g/2 \right) \) and \(\delta^*_\text{ch}=\arctan\left( \pi u/2 \right) \). In the small coupling limit, these can be approximated as \(\delta^*_\text{sp}=\pi g/2\) and \(\delta^*_\text{ch}=\pi u/2\).
\item We now focus on the critical point \(g = -4u\) of our model. At this point, the phase shifts get related to each other: \(\delta^*_\text{sp} = -4\delta^*_\text{ch}\), so that the exponent of the self-energy takes the form
	\begin{equation}\begin{aligned}
		\gamma_{dd} \simeq 1 - \frac{3}{\pi}\delta^*_\text{ch} = 1 + \frac{3}{8}\alpha
	\end{aligned}\end{equation}
	where we have used the fact that for our model, the effective pseudogap parameter \(\alpha\) is set to \(-4u\). The local self-energy then vanishes as
	\begin{equation}\begin{aligned}
		\Sigma_{dd} \sim |\omega|^{1 + \frac{3}{8}\alpha}
	\end{aligned}\end{equation}
	This can be compared with the expression \(\sim|\omega|^{2-3\alpha}\) of the impurity self-energy obtained in ref.~\cite{fritzvojta2004}.
\item In a similar manner, the self-energy \(\Sigma_{d0}\) for scattering processes that connect the impurity site and the bath zeroth site can also be obtained. The exponent \(\gamma_{d0}\) for this self-energy is given by \(\gamma_{d0} = 2 - 2\gamma_{dd}\), so that this non-local self-energy diverges as
	\begin{equation}\begin{aligned}
		\Sigma_{d0} \sim |\omega|^{- \frac{3}{4}\alpha}
	\end{aligned}\end{equation}
\item By using our tiling approach, the \(k-\)space self-energy at the critical point can be written as
	\begin{equation}\begin{aligned}
		\Sigma(\vec k,\omega) = \Sigma_{dd} + \frac{1}{\mathcal{W}}\xi_{\vec k}\Sigma_{d0}
	\end{aligned}\end{equation}
	This expression suggests that at the critical point, all points in the Brillouin zone except those at the Fermi surface get gapped out.
